Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-24 paper.tex
adding ackknowledgments
typo
removing a dealt comment

Regarding the uncertainty, disregarding the artefact of a very low mean inventory
observed at the onset of fissile material production, the relative uncertainty
starts at about $5\%$, and grows until year
125 to decrease to $10\%$ at the end of the simulation time (180y), it seems
%% I don't see what you mean by decrease up to 10%?
it would have reached an equilibrium between $5$ and $10\%$ with longer
simulations...
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length.  As with the uranium needs, different cycle length
implies different number of fuel loads, so different amount of resources used.  Never the less, around year 65 (see Figure
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
small enough to start limiting production of fissile material.
The uncertainty weight is then slowly transferred from
the cycle length to the fuel cooling time.

>>>>

Regarding the uncertainty, disregarding the artefact of a very low mean inventory
observed at the onset of fissile material production, the relative uncertainty
starts at about $5\%$, and grows until year
125 to decrease to $10\%$ at the end of the simulation time (180y), it seems
it would have reached an equilibrium between $5$ and $10\%$ with longer
simulations...
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length.  As with the uranium needs, different cycle length
implies different number of fuel loads, so different amount of resources used.  Never the less, around year 65 (see Figure
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
small enough to start limiting the production of fissile material.
The uncertainty weight is then slowly transferred from
the cycle length to the fuel cooling time.
